### 2024-07-29 short/sections/future-papers.tex
Update future-papers.tex

\item{Kantorowicz, J., \& González-Bustamamante, B. (2024, {\itshape forthcoming}). {\itshape The Changing Concepts of the Rule of Law}. Presentation delivered at the 6th Annual COMPTEXT Conference, Amsterdam, Netherlands.}\vspace{1mm}

\item{González-Bustamamante, B., \& Kantorowicz, J. (2024, {\itshape forthcoming}). {\itshape Multilingual Word Embeddings for Unravelling the Rule of Law in European Countries}. Presentation delivered at the 6th Annual COMPTEXT Conference, Amsterdam, Netherlands.}\vspace{1mm}

>>>>

\item{González-Bustamante, B., \& Rivera, S. (2024, {\itshape forthcoming}). Toxicity and Digital Incivility during Political Deliberation: The Case of the Constitutional Convention in Chile. Paper delivered at the Digital Democracy Workshop, Digital Society Initiative, University of Zurich, Zurich, Switzerland.}\vspace{1mm}

\item{González-Bustamante, B. (2024, {\itshape forthcoming}). Benchmarking Open-Source Large Language Models in Political Content Text-Annotation: Proof-of-Concept with Toxicity and Incivility Data. Preprint.}\vspace{1mm}

\item{Kantorowicz, J., \& González-Bustamamante, B. (2024). {\itshape The Changing Concepts of the Rule of Law}. Paper delivered at the 6th Annual COMPTEXT Conference, Amsterdam, Netherlands.}\vspace{1mm}

\item{González-Bustamamante, B., \& Kantorowicz, J. (2024). {\itshape Multilingual Word Embeddings for Unravelling the Rule of Law in European Countries}. Paper delivered at the 6th Annual COMPTEXT Conference, Amsterdam, Netherlands.}\vspace{1mm}
